TacticToe: Learning the Game of Tactics

### 2018-01-21 tactictoe_jv.tex
search: search tree definition

\begin{align*}
D_0 &=_{def} \lbrace f \rbrace \\
D_{n+1} &=_{def} D_n \cup \lbrace (t,g)\in \mathfrak{F}\  |\ \exists 
(\hat{t},\hat{g}) \in D_n.\ g \in \hat{t}(\hat{g}) \rbrace  \\
D_\infty &=_{def} \bigcup_{i \in \mathbb{N}^*} D_i\\
\end{align*}
where $\hat{t}(\hat{g})$ denotes the resulting set of goals produced by the 
application 
of the tactic $\hat{t}$ to the goal $\hat{g}$.
\end{definition}

@@

\begin{definition}(Tactical search tree)
A tactical search tree (or search tree) is a set of nodes containing a list of 
goals where each goal $g$ of a node $n$ is linked to a node $m$ when the list 
of 
\end{definition}

@@

\begin{definition}(Solved node and solved goal)
Let $\mathbb{T}$ be a search tree. The set of solved nodes $\mathbb{A}^*$ and 
the set of solved goals $\mathbb{G}^*$ are the smallest set verifying the 
following equations:

\todo{should I make a constructive definition with $A^n+1$ in terms of $G^n$ 
instead?}
\begin{align*}
\mathbb{A}^* &= \lbrace a \in \mathbb{A}\ |\ \forall g \in G(a).\ g \in 
\mathbb{G}^* \rbrace\\
\mathbb{G}^* &= \lbrace g \in \mathbb{G}\ |\ \exists t \in T(g).\ t(g) \in 
\mathbb{A}^* \rbrace
\end{align*}

@@

\subsection{Prior tactic policy}

The estimation through the distance produced by the tactic selectors are hard 
to translate into a prior tactic policy, so we rely only on the order of 
tactics to estimate the probability with which a tactic should be tried.
Let $t_0,\ldots,t_500$ be the list of preselected tactics ordered by their 
distance to a goal $g$. Let $c_policy$ be a constant heuristic that estimates 
how likely a tactic $t_i$ is to prove the goal compared to the rest of the 
tactics $t_{i+1},\ldots,t_500$. We make the strong assumption that $c_policy$ 
is constant across the search. We can now calculate the prior policy by:

\[PriorPolicy(t_{i}) = (1 - c_policy)^{i} * c_policy\]

>>>>

\begin{align*}
D_0 &=_{def} \lbrace f \rbrace \\
D_{n+1} &=_{def} D_n \cup \lbrace (t,g)\in \mathfrak{F}\  |\ \exists 
(\hat{t},\hat{g}) \in D_n.\ g \in \hat{t}(\hat{g}) \rbrace  \\
D_\infty &=_{def} \bigcup_{i \in \mathbb{N}} D_i\\
\end{align*}
where $\hat{t}(\hat{g})$ denotes the resulting set of goals produced by the 
application 
of the tactic $\hat{t}$ to the goal $\hat{g}$.
\end{definition}

@@

\begin{definition}(Tactical search tree)\\
A tactical search tree is a sixtuple $(\mathbb{A},\mathbb{G},\mathbb{T},A,G,T)$ 
that respects the following conditions:
\begin{itemize}
\item $\mathbb{A}$ is a set of nodes, $\mathbb{G}$ is a set of goals 
 and $\mathbb{T}$ is a set of tactics.
\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to 
$\mathbb{A}$.
\item $T$ is a total function from $\mathbb{G}$ to $P(\mathbb{T})$.
\item $G$ is a total function from $\mathbb{A}$ to $P(\mathbb{G})$.
\item $Support(A) = \lbrace (g,t)\ |\ t \in T(g) \rbrace$.
\item if $t \in T(g)$ and $A(g,t) = a$ then $t(g) = G(a)$.
\end{itemize}

Additional constraints such as acyclicity and the fact that there is exactly 
one root node are properties of this graph that are preserved during the 
application of the MCTS algorithm. That is why we call it a tree although this 
we do not specify it in this definition.
\end{definition}

We assume that any set is numbered and that we can access a nth member of set 
$s$ by writing $s_n$. For readability in the next figure $(G(a_j))_i$ is 
written 
$g_j^i$.

@@

\begin{definition}(Solved node and solved goal)
Let $\mathbb{T}$ be a search tree. The set of solved nodes $\mathbb{A}^\infty$ 
and 
the set of solved goals $\mathbb{G}^\infty$ are defined inductively by:

\begin{align*}
\mathbb{A}^{0} &=_{def} 
\lbrace a \in \mathbb{A}\ |\ G(a) = \emptyset \rbrace \\ 
\mathbb{G}^{0} &=_{def} \lbrace g \in \mathbb{G}\ |\ 
\exists a \in A(g).\ a \in \mathbb{A}^{0} \rbrace\\
\mathbb{A}^{n+1} &=_{def} \lbrace a \in \mathbb{A}\ |\ 
\forall g \in G(a).\ g \in \mathbb{G}^{n} \rbrace\\
\mathbb{G}^{n+1} &=_{def} \lbrace g \in \mathbb{G}\ |\ 
\exists a \in A(g).\ a \in \mathbb{A}^{n+1} \rbrace \\
\mathbb{A}^\infty &=_{def} \bigcup_{i \in \mathbb{N}} \mathbb{A}^n\\
\mathbb{G}^\infty &=_{def} \bigcup_{i \in \mathbb{N}} \mathbb{G}^n\\
\end{align*}

@@

\subsection{Prior tactic policy}
The estimation through the distance produced by the tactic selectors are hard 
to translate into a prior tactic policy, so we rely only on the order of 
tactics to estimate the probability with which a tactic should be tried.
Let $t_0,\ldots,t_500$ be the list of preselected tactics ordered by their 
distance to a goal $g$. Let $c_{policy}$ be a constant heuristic that estimates 
how likely a tactic $t_i$ is to prove the goal compared to the rest of the 
tactics $t_{i+1},\ldots,t_500$. We make the strong assumption that $c_policy$ 
is constant across the search. We can now calculate the prior policy by:

\[PriorPolicy(t_{i}) = (1 - c_{policy})^{i} * c_{policy}\]
